---
title: "ARCH/GARCH Modelling"
output: html_document
date: "2023-10-06"
---

```{r}
library(quantmod)
getSymbols("NFLX", src = "yahoo")

head(NFLX)

```

```{r}
nflx_df <- data.frame(Date = index(NFLX), coredata(NFLX))

# Rename the columns for clarity
names(nflx_df) <- c("Date", "Open", "High", "Low", "Close", "Volume", "Adjusted")

nflx_df <- nflx_df[c('Date' , 'Adjusted')  ] 

head(nflx_df)
```

```{r}

# Assuming you have a dataframe nflx_df with columns Date and Adjusted

# Ensure the data is sorted by Date
nflx_df <- nflx_df[order(nflx_df$Date), ]

# Convert the 'Adjusted' prices to a time series object
# Assuming daily data and starting year is 2007 (modify this according to your data)
start_year <- as.numeric(format(min(nflx_df$Date), "%Y"))
start_month <- as.numeric(format(min(nflx_df$Date), "%m"))
nflx_ts <- ts(nflx_df$Adjusted, start = c(start_year, start_month), frequency = 252)

head(nflx_ts)

```

```{r}
# Plotting the nflx_ts time series
plot(nflx_ts, xlab = "Time", ylab = "Adjusted Price", main = "Netflix Stock Prices Over Time", col = "blue", type = "l")

# Adding a grid for better readability
grid(nx = NULL, ny = NULL, col = "gray", lty = "dotted")

```

Visually, the series exhibits a clear upward trend, especially noticeable from around 2012 onwards, with significant volatility and a pronounced spike before a substantial drop. This behavior suggests that the time series is non-stationary, as it does not exhibit a constant mean over time. The variance also appears to be changing, with periods of higher volatility, particularly in later years. For ARCH/GARCH modeling, which assumes stationarity, differencing the series or modeling the mean as a function of time might be necessary to stabilize the mean before applying volatility models. 

```{r}
acf(nflx_ts, main="ACF for NFLX Time Series")
```

ACF on differenced data

```{r}
# Plot ACF of the differenced time series
acf(diff(nflx_ts), main="ACF for Differenced NFLX Time Series")

```

PACF
```{r}
pacf(nflx_ts, main="PACF for NFLX Time Series")
```

```{r}
library(forecast)

best_arima_model <- auto.arima(nflx_ts)

# Look at the summary of the model
summary(best_arima_model)
```

```{r}

residuals_arima <- residuals(best_arima_model)
# Plot the residuals
plot(residuals_arima, main="Residuals of ARIMA Model", ylab="Residuals", xlab="Time")

```


```{r}
library(lmtest)

data <- data.frame(residuals=residuals, index=1:length(residuals))

# Fit a linear model - as the Breusch-Pagan test requires a linear model object
lm_model <- lm(residuals ~ index, data=data)

# Perform the Breusch-Pagan test
bp_test <- bptest(lm_model)

# Output the result of the Breusch-Pagan test
print(bp_test)
```

```{r}
squared_residuals <- residuals^2

# Use the acf function to compute the ACF of the squared residuals
par(mar=c(5, 4, 4, 2) + 0.1)
acf(squared_residuals, main="ACF of Squared Residuals")
```

```{r}
library(tseries)
library(fGarch)
```

```{r}
residuals <- na.omit(residuals)  # Remove NA values
residuals <- residuals[is.finite(residuals)]  # Remove Infinite values
residuals <- scale(residuals)
arch.fit <- garchFit(~garch(1,0), data = residuals, trace = F)
summary(arch.fit)
```

```{r}
# Assuming you have successfully fitted the ARCH model and stored it in arch.fit
# Plot the residuals from the ARCH model
plot(arch.fit@residuals, main = "Residuals of the GARCH Model", ylab = "Residuals", xlab = "Time")

```


